Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Coleoptera: Curculionid{\ae}), with notes on their distribution and phylogeny

### 2018-03-14 tex/manuscript.tex
finalized tree, most of manuscript, refs

\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{textcomp}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}

\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 (Coleoptera: Curculionid\ae), with notes on their distribution and phylogeny}

@@

% \keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

@@

\section*{Introduction}
	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863, subtribe Tanymecina Lacoirdaire, 1863 (Curculionidae: Entiminae). 
	The genus was recently revised and includes a total of 17 described species distributed throughout the desert and plains regions of North America.
	Since the publication of our monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
	Here we describe these species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus}, based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} is given along with information on the geographic distribution of the herein described species.
	Where possible, we make note of host-plant records and briefly consider the historical biogeographic relationships of the new species.
	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision.

\section*{Materials and methods}
	The keen reader will note the alignment of the methods used in this manuscript with those of Jansen and Franz 2015. 
	For convenience and transparency, we provide an updated account of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.

	\paragraph{Natural history observations} 
		Members of the genus \textit{Minyomerus} may be found on a variety of host plants, as indicated following each description.
		While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
		Members of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico. 
		The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.

	\paragraph{Acquisition of museum specimens} 
		Georeferencing of localities was performed with Google Earth (Google Inc. 2009–2015) and reported in decimal degrees.
		Taxonomic names for associated host plants are used in accordance with Munz and Keck (1973) and SEINet (2017).
		The existing set of \textit{Minyomerus} specimens used in the revision of Jansen and Franz 2015 was supplemented with material from the following collections, using the codens of Arnett et al. (1993):

@@

	\paragraph{Morphological analysis}
		Our systematic and descriptive approach is complementary to Jansen and Franz 2015, which in turn follows Franz (2010a, 2010b, 2012).
		Terminology for exterior morphology is in general accordance with Torre-Bueno (Nichols 1989).
		Additional morphological terms specific to (entimine) weevils were used as follows:
			Ting (1936) and Morimoto and Kojima (2003) for mouthparts;
			Thompson (1992) for tibial apices and abdominal segments;
			and Oberprieler et al. (2014) and Howden (1995) for male and female terminalia.

		Measurements were taken with a Leica M205 C stereomicroscope and associated software, Leica Application Suite (LAS), version 4.1.0.
		Overall body length and width were measured in dorsal view as the maximum distance between the rostral and elytral apices, and the maximum width of both elytra, respectively.
		Rostral length was measured in dorsal view as the distance between the epistomal apex and the anterior margin of the eyes.
		Rostral width was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
		Pronotal length was measured in dorsal view as the length along the midline between the anterior and posterior margins.
		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.

		Herein recognized species of \textit{Minyomerus}  were delimited through application of the phylogenetic species concept \textit{sensu} Wheeler and Platnick (2000).
		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		The key to identifying species of \textit{Minyomerus} is arranged with emphasis being placed on the most readily observable diagnostic characters.
		This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

	\paragraph{Phylogenetic analysis}
		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} sec. Jansen and Franz (2015) and four newly recognized species.
		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup (Jansen and Franz 2015, Nixon and Carpenter 1993).
		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] (Alonzo-Zarazaga and Lyal 1999).
		Thus, four of the five outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz. Isodacrys buchanani Howden, 1961 [non-focal], Isodrusus debilis Sharp, 1911 [non-focal], Pandeleteinus subcancer Howden, 1969 [non-focal], and Pandeleteius cinereus (Horn, 1876) [non-focal].
		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration (Rieppel 2007; Franz 2014).
		To this end we used the North American species Sitona californicus (Fahraeus, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].

		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively (Nixon 2002).
		The character sequence follows that of the taxonomic descriptions.
		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA (Goloboff 1999).
		An unconstrained heuristic search was conducted using the commands: \texttt{hold 100001}, \texttt{mult*1000}, \texttt{hold/100}, with \texttt{mult*max*} selected.
		Bootstrap support was inferred in WinClada using the parameters of \texttt{1000 replications}, \texttt{hold 1000}, \texttt{hold/100}, \texttt{mult*10}, \texttt{Don’t do max*}, and \texttt{Save consensus}.
		Finally, Bremer support values (Bremer 1994) were calculated in NONA using the commands: \texttt{hold 20000}, \texttt{suboptimal 20}, and \texttt{bsupport 20}.

	\paragraph{Species distribution modeling}
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs.~\#) based on documented occurrence records (Phillips et al. 2004, 2006; Elith et al. 2011).
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005).
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling (Quantum GIS Development Team 2017).

		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders (Hijmans et al. 2012).

@@

	\subsection*{\textit{Minyomerus ampullaceus} - sp. n.}

@@

			Due to the relatively poor condition of the scales and setae of the holotype, color and setation cannot be reliably used for identification.
			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4 as wide as long in dorsal view.
			In lateral view the anterior and posterior declivities of the elytra are strongly abrupt, and nearly vertical; most notably, the anterior magin of the elytra projects strongly and characteristically dorsad of its articulation with the posterior pronotal margin.

@@

				Setae recumbent to sub-recumbent, white to brown in color.

@@

				Partially covered with white, slightly opalescent scales, with 3 longer setae, and 1 shorter seta between these.

@@

				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibrissae. 

@@

			\paragraph{Antennae}

@@

				Pronotum in lateral view with setae that reach beyond anterior margin by 1/2 of their length; these setae becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye. 
				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibrissae achieving a maximum length similar to anterior-posterior length of eye.

@@

				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae. 

@@

				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform setae.

@@

				Posterior declivity angled at nearly 85\td to main body axis. Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.

@@

			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [Cuculidae], the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).

@@

	\subsection*{\textit{Minyomerus franko} - sp. n.}

@@

			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long setae of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
			In addition, the setae lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.

@@

			The aedeagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.

@@

				Setae linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.

@@

				Covered with white scales, with 3 longer setae, and 1-2 shorter setae between these.
			\paragraph{Maxillae}

@@

region, setae covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 

@@

				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.

@@

				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate , with 2 large vibrissae. 

@@

				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect setae.

@@

				Pronotum in lateral view with setae that reach just beyond anterior margin, angled laterally at 45-80\td to longitudinal axis, and strikingly long; these setae becoming evenly longer and more angled laterally, reaching a maximum length nearly equal to length of eye. 
				Anterolateral margin with a reduced tuft of 5 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3\x anterior-posterior length of eye, except for one vibrissa achieving a maximum length similar to anterior-posterior length of eye.

@@

				Metatibial apex with almond shaped convexity ringed by 8-9 short, spiniform setae.

@@

				Spiculum gastrale 2\x length of aedeagal pedon. Laminar alae located on lateral 1/4 of posterior margin.

>>>>

\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{textcomp}
\usepackage{array}
\usepackage{xtab}
\usepackage{dcolumn}
\usepackage{multirow}
\newcolumntype{m}[1]{D{.}{~}{#1}}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}
\newcommand{\breakfill}{\dotfill\newline\penalty0\hbox{}\nobreak\dotfill}

\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Coleoptera: Curculionid{\ae}), with notes on their distribution and phylogeny}

@@

%\keywords{Biogeography, cladistics, concept taxonomy, desert, Entiminae, \textit{Minyomerus}, new species, provenance, weevils} - KEYWORDS PROVIDED DURING SUBMISSION.

\begin{abstract}
	This contribution adopts the taxonomic concept annotation and alignment approach. 
	Accordingly, and where indicated, previous and newly inferred meanings of taxonomic names are individuated according to one specific source.
	Articulations among these concepts and pairwise, logically consistent alignments of original and revisionary classifications are also provided, in addition to conventional nomenclatural provenance information. 
	Descriptions of four species belonging to the broad-nosed weevil genera \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) are presented.
	Prior to this study, \textit{Minyomerus} sec. Jansen \& Franz, 2015 contained 17 species species distributed throughout the desert and plains regions of North America.
	We thoroughly describe these four species as new to science: \textit{M. ampullaceus} sec. Jansen \& Franz (2015) (henceforth: [JF2015]), sp. n., \textit{M. franko} [JF2015], sp. n., \textit{M. sculptilis} [JF2015], sp. n., and \textit{M. tylotos} [JF2015], sp. n. 
	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (L = 99, CI = 60, RI = 80). 
	The analysis supports the monophyly of Minyomerus [JF2015] with eight unreversed synapomorphies, in corroboration of prior work.
	Accordingly, each of the four new species is placed within \textit{Minyomerus} [JF2015], and their species-group placement, possible biogeographic origins, and natural history are discussed in detail.
\end{abstract}

@@

\section*{Introduction}
	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2015] is currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionid{\ae} [non-focal]: Entimin{\ae} [non-focal] - higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}). 
	A recent phylogenetic revision of the genus recognized a total of 17 described species distributed throughout the desert and plains regions of North America \citep{jansen2015}.

	Members of the genus \textit{Minyomerus} [JF2015] are phytophagous, and may be found on a variety of host plants, especially the creosote bush (\textit{Larrea tridentata} (DC.) Coville [non-focal; Zygophyllaceae [non-focal]), broomweed (\textit{Gutierrezia lagasca} [non-focal; Asteraceae [non-focal), sagebrush (\textit{Artemisia} Linnaeus [non-focal]; Asteraceae [non-focal]), and occasionally on other various Asteraceae [non-focal] \citep{jansen2015}. 
	While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
	Species of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts; however, their range extends throughout the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico \citep{obrien1982, jansen2015}. 
	The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.

	\textit{Minyomerus} [JF2015] belongs to the broad-nosed weevils, subfamily Entimin{\ae} [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
	They are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales (`set{\ae}') arranged in rows on the elytral intervals, and can range in length from 2.8 to 6.0 mm \citep{jansen2015}.
	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibriss{\ae} that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.

	The genus is diagnosed by a unique combination of synapomorphic traits, described by \citet{jansen2015}, and as follows:

	\begin{enumerate}[itemsep=-0.4em]
		\item The integument is covered by appressed scales that are sub-circular and overlap posteriorly.
		\item The nasal plate is present as a broad, scale-covered, chevron-shaped ridge demarcating the epistoma.
		\item A sulcus posteriad of nasal plate is present.
		\item The scrobe is sub-equal in length to the funicle and club combined.
		\item The head is directed slightly ventrally.
		\item The metatibial apex lacks setiform bristles yet displays bristles that are shorter to sub-equal in length to the surrounding set{\ae} and conical to lamelliform.
		\item The mesotarsi are slightly shorter than the mesotibi{\ae}.
		\item All tarsi lack pads of setiform set{\ae} but have stout, spiniform set{\ae}.
	\end{enumerate}

	The following additional characters are useful for identifying members of \textit{Minyomerus} [JF2015], especially when differentiating the former from other genera of Tanymecini [non-focal] that may be found together in the same desert habitats, viz. \textit{Isodrusus} Sharp, 1911 [non-focal], \textit{Isodacrys} Sharp, 1911 [non-focal], and \textit{Pandeleteinus} Champion, 1911 [non-focal] (see also \citealt{anderson2002}):

	\begin{enumerate} [itemsep=-0.4em]
		\item The intercoxal process of the prosternum is medially divided into two halves, with the procox{\ae} apparently contiguous in most.
		\item The elytral humeri are rounded rather than angled and protruding.
		\item The profemora are not dilated and lack spines.
		\item The protibi{\ae} are ventrally excavated by a longitudinal groove or concavity.
		\item A distinct scrobe is present and directed ventrad of the eye, with a more or less apparent tooth formed by an overhang of the dorsal margin.
	\end{enumerate}

	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet well circumscribed by the generic delimitation of the genus.
	As such, the addition of these new species \emph{does not} alter the definition of the genus (see Phylogenetic results), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
	For ease of legibility, especially when discussing differences in clade composition when comparing between this and previous work, we use the notation [JF2015] and [JF2018] to specify taxon concepts sec. Jansen \& Franz, 2015 and sec. Jansen \& Franz, 2018, respectively.
	Specifically, all clades inferred in this work will be designated according to the concept [JF2018], \emph{unless} there is perfect congruence (viz. synapomorphies and clade composition) with a clade previously resolved by \citet{jansen2015}, in which case the identifier [JF2015] will be retained.
	While this is the case for all of the previously described species, and a few select clades, we differentiate the newly inferred clade corresponding to the genus, and including the herein described species, as \textit{Minyomerus} [JF2018].

	Here we describe the four newly found species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2015], based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} [JF2015] is given along with an updated checklist of the genus.
	Where possible, we make note of host-plant records and briefly consider the geographic distribution of the herein described species.
	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision \citep{jansen2015}.

\section*{Materials and methods}
	In order to maximize the compatibility of the new species accounts with the higher-level generic account of \textit{Minyomerus} [JF2015], the methods used in this manuscript are aligned with those of \citet{jansen2015}.
	Here we provide an updated account of the procedures used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.

	\subsection*{Acquisition of museum specimens} 
		The existing set of \textit{Minyomerus} [JF2015] specimens used in the revision of \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:

@@

			Georeferencing of localities was performed with Google Earth \citep{google2018} and reported in decimal degrees.
		Taxonomic names for associated host plants, as noted following each species account, are used in accordance with \citet{munz1973} and \citet{seinet2018}.

	\subsection*{Morphological analysis}
		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
		Terminology for exterior morphology is in general accordance with \citet{torre1989}.
		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
			\citet{thompson1992} for tibial apices and abdominal segments;
			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.

		Measurements were taken with a Leica M205 C stereomicroscope and associated software, Leica Application Suite (LAS), version 4.1.0.
		Overall body length and width were measured in dorsal view as the maximum distance between the rostral and elytral apices, and the maximum width of both elytra, respectively.
		Rostral length was measured in dorsal view as the distance between the epistomal apex and the anterior margin of the eyes.
		Rostral width was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
		Pronotal length was measured in dorsal view as the length along the midline between the anterior and posterior margins.
		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and {\ae}deagus).
		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.

		Herein recognized species of \textit{Minyomerus} [JF2015] were delimited through application of the phylogenetic species concept \textit{sensu} \citet{wheeler2000}.
		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
		As in \citet{jansen2015}, the species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus} [JF2015].
		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		The key to identifying species of \textit{Minyomerus} [JF2015] is arranged with emphasis being placed on the most readily observable diagnostic characters.
				This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

	\subsection*{Phylogenetic analysis}
		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} [JF2015] and four newly recognized species.
		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup \citep{jansen2015, nixon1993}.

		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] \citep{alonso1999}.
		Thus, four of the five outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz. \textit{Isodacrys buchanani} Howden, 1961 [non-focal], \textit{Isodrusus debilis} Sharp, 1911 [non-focal], \textit{Pandeleteinus subcancer} Howden, 1969 [non-focal], and \textit{Pandeleteius cinereus} (Horn, 1876) [non-focal].
		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration \citep{rieppel2007, franz2014}.
		To this end we used the North American species \textit{Sitona californicus} (Fahr{\ae}us, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].

		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively \citep{nixon2002}.
		The character sequence follows that of the taxonomic descriptions.
		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA \citep{goloboff1999}.
		An unconstrained heuristic search was conducted using the commands: \texttt{hold 100001}, \texttt{mult*1000}, \texttt{hold/100}, with \texttt{mult*max*} selected.
		Bootstrap support was inferred in WinClada using the parameters of \texttt{1000 replications}, \texttt{hold 1000}, \texttt{hold/100}, \texttt{mult*10}, \texttt{Don’t do max*}, and \texttt{Save consensus}.
		Finally, Bremer support values \citep{bremer1994} and relative fit difference \citep{goloboff2001} were calculated in NONA using the commands: \texttt{hold 1001}, \texttt{sub 20}, \texttt{bs} for Bremer support values, and \texttt{bs*} for relative fit difference, respectively \citep{goloboff2008}.

		The motivation for providing Bremer support values and relative fit difference comes from their respective interpretations, based on how the measures are calculated, \textit{per} \citet{goloboff2001}.
		Both of these indices rely on summation of the number of favorable and contradictory characters when comparing a most-parsimonious tree to a suboptimal tree. 
		If the step length of the $i^{\text{th}}$ character ($I$) of $n$ total characters on the most-parsimonious tree ($L_{MPT}$) is less than its corresponding step length on the suboptimal tree ($L_{SUB}$), the character is designated as favorable ($f_{i}$), but if the opposite is true, the character is designated as contradictory ($c_{i}$), and expressed formally:
		\begin{equation}
		I = 
			\begin{cases}
				f_{i} & L_{MPT} < L_{SUB}\\
				c_{i} & L_{MPT} > L_{SUB}
			\end{cases}
		\end{equation}
		Where the number of favorable ($F$) and contradictory ($C$) characters are defined, respectively, as:
		\begin{align}
			F = \sum_{n = 0}^{i}{f_{i}}\\
			C = \sum_{n = 0}^{i}{c_{i}}
		\end{align}
		Bremer support values (bsv) and relative fit difference (rfd) are then calculated simply as:
		\begin{align}
			\text{bsv} & = F - C\\
			\text{rfd} & = \frac{F - C}{F} \times 100
		\end{align}

		The Bremer support value for a node thus indicates how many more characters support a node than contradict it, while the relative fit difference indicates what proportion of the favorable characters are represented by the Bremer support value.
		Whereas the Bremer support value is as large as the number of characters supporting the node, in excess of the contradicting characters, the relative fit difference can only vary from 0 to 100, as a proportion of the number of supporting characters.
		By providing both measures, one may quickly discriminate, for example, between a node supported by 4 characters but contradicted by 1 character (bsv = 3, rfd = 75), and a node supported by 10 characters but contradicted by 7 characters (bsv = 3, rfd = 30).

	\subsection*{Species distribution modeling}
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\#) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.

		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.

@@

	\subsection*{\textit{Minyomerus ampullaceus} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}

@@

			Due to the relatively poor condition of the scales and set{\ae} of the holotype, color and setation cannot be reliably used for identification.
			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4\x as wide as long in dorsal view.
			In lateral view the anterior and posterior declivities of the elytra are strongly abrupt, and nearly vertical; most notably, the anterior margin of the elytra projects strongly and characteristically dorsad of its articulation with the posterior pronotal margin.

@@

				Set{\ae} recumbent to sub-recumbent, white to brown in color.

@@

				Partially covered with white, slightly opalescent scales, with 3 longer set{\ae}, and 1 shorter seta between these.

@@

				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibriss{\ae}. 

@@

			\paragraph{Antenn{\ae}}

@@

				Pronotum in lateral view with set{\ae} that reach beyond anterior margin by 1/2 of their length; these set{\ae} becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye. 
				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibriss{\ae} achieving a maximum length similar to anterior-posterior length of eye.

@@

				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}. 

@@

				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform set{\ae}.

@@

				Posterior declivity angled at nearly 85\td to main body axis. Elytra with 10 complete stri{\ae}; stri{\ae} shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.

@@

			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829 [non-focal]; Cuculid{\ae} [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).

@@

	\subsection*{\textit{Minyomerus franko} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}

@@

			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long set{\ae} of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
			In addition, the set{\ae} lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.

@@

			The {\ae}deagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.

@@

				Set{\ae} linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.

@@

				Covered with white scales, with 3 longer set{\ae}, and 1-2 shorter set{\ae} between these.
			\paragraph{Maxill{\ae}}

@@

region, set{\ae} covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 

@@

				I apically oblique, apical end forming a 45\td angle with base, with 2 apical set{\ae}; II sub-cylindrical, with 1 apical seta.

@@

				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate , with 2 large vibriss{\ae}. 

@@

				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect set{\ae}.

@@

				Pronotum in lateral view with set{\ae} that reach just beyond anterior margin, angled laterally at 45-80\td to longitudinal axis, and strikingly long; these set{\ae} becoming evenly longer and more angled laterally, reaching a maximum length nearly equal to length of eye. 
				Anterolateral margin with a reduced tuft of 5 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} sub-equal in length at 1/3\x anterior-posterior length of eye, except for one vibrissa achieving a maximum length similar to anterior-posterior length of eye.

@@

				Metatibial apex with almond shaped convexity ringed by 8-9 short, spiniform set{\ae}.

@@

				Spiculum gastrale 2\x length of {\ae}deagal pedon. Laminar al{\ae} located on lateral 1/4 of posterior margin.
